\Large \bf Relationship of Weather and Maize Yields in Kenya

### 2018-11-16 writing/draft1/draftMonika10.tex
workiing more and more
writing bullet points

\FloatBarrier
	\section{Results and discussion}\label{Results}

@@

\item Tables of estimates of:

@@

\end{enumerate}
\item Verbal description and interpretation of the results in table
\item Discussion and Conclusion:
	\begin{itemize}
	\item Stressing the importance of not only focusing on prediction of rain totals, but also other characteristics of the weather - particularly the variables found significant
	\end{itemize}
	\item \textcolor{red}{Caveats}
\end{itemize}
\color{black}

>>>>

\FloatBarrier
	\section{\textcolor{black}{Results and discussion}}\label{Results}

@@

\item Tables of estimates:

@@

\end{enumerate}
\item Verbal description and interpretation of the results in table
\item Discussion and Conclusion:

	\end{itemize}
\section{Conclusion}\label{Conclusion}

	\begin{itemize}
	\item Besides seasonal totals (averages), there are many weather/climate characteristics (measures) which are important for yield
	\item  Current weather and climate forecasts (in the context of disaster management) are mostly focused on totals in precipitation (and average temperature?) 
	\item There is a strong movement to shift the focus from forecasting merely weather/climate to forecast of weather/climate and its impacts

	\begin{itemize}
	\item[$\boldsymbol{\rightarrow}$] We can stress the importance of focusing the forecast on the climate characteristics (or measures) which we find significant in our models
\end{itemize}

	\item \textcolor{red}{Caveats}

	\begin{itemize}
	\item\textcolor{red}{ Yield data: Is the collection method consistent over time and space?}
	\item Livestock
	\item Cropping calendar is likely to differ across the country

	\end{itemize}
\end{itemize}
\color{black}
